Type-Safe Modular Parsing

### 2017-01-10 paper/sections/Inheritance.tex
Parsing

\subsection{Multiple Extensions and Independent Extensibility}
A nice feature of Scala is its support for a form of multiple inheritance.
Scala has a linearized-style multiple inheritance for traits~\cite{}. 
This can be very helpful when composing several languages, which 
may have been independently developed. Suppose now
we want to compose the parsers for expressions from pre-defined
languages \inlinecode{LanguageA} and \inlinecode{LanguageB} using
alternative.\bruno{Don't be abstract! Use concrete examples. You 
already have Var, maybe you can add another language extension for 
boolean literals. Show the code for the boolean literals parsing as
well as the composition code.}
The use of keyword \inlinecode{super} is able to
specify the implementation from inheritance, like:

>>>>

\subsection{Multiple Extensions and Independent Extensibility}
A nice feature of Scala is its support for a form of multiple inheritance.
Scala has a linearized-style multiple inheritance for traits~\cite{}. 
This can be very helpful when composing several languages, which 
may have been independently developed. Suppose now
we want to compose the parsers for expressions from pre-defined
languages \inlinecode{LanguageA} and \inlinecode{LanguageB} using
alternative.\bruno{You can present the abstract example, as you do
  here, but you should also present a concrete example. You 
already have Var, maybe you can add another language extension for 
boolean literals. Show the code for the boolean literals parsing as
well as the composition code.}
The use of keyword \inlinecode{super} is able to
specify the implementation from inheritance, like:
